Automated Program Verification and Synthesis of Embedded \& Cyber-physical Systems: Advances and Challenges

### 2017-08-03 paper.tex
reviewed section 3
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

Indeed, given a transition system \textit{M}, which is derived from the control-flow graph of a program, a property $\phi$, which represents program correctness and/or a system's behavior, and an iteration bound \textit{k}, which limits loop unrolling, data structures, and context-switches, BMC techniques thus unfold a system \textit{k} times, in order to convert it into a verification condition $\psi$, which is expressed in propositional logic or in a decidable-fragment of first-order logic, such that $\psi$ is \textit{satisfiable} if and only if $\phi$ has a counterexample of depth less than or equal to \textit{k}. The propositional problem associated with SAT-based BMC is formulated by constructing the following formula~\cite{Biere99}:
%
\begin{equation}
\label{bounded-model-checking-biere}
\psi_{k} = I\left(s_{0}\right) \wedge \bigwedge^{k-1}_{i=0} R\left(s_{i},s_{i+1}\right) \wedge \neg \phi_{k}
\end{equation}

\noindent Here, $\phi_{k}$ represents a safety property $\phi$ in step $k$, $I$ is the set of initial states of $M$, $R\left(s_{i},s_{i+1}\right)$ is the transition relation of $M$ at time steps $i$ and $i+1$. Hence, the formula $\bigwedge^{k-1}_{i=0} R\left(s_{i},s_{i+1}\right)$ represents the set of all executions of $M$ of length $k$. $\neg \phi_{k}$ represents the condition that $\phi$ is violated in state $k$, which is reached by a bounded execution of $M$ of length $k$. Finally, the resulting (bit-vector) formula is translated to conjunctive normal form in linear time and passed to a SAT solver for checking satisfiability. Formula (\ref{bounded-model-checking-biere}) can be used to check safety properties~\cite{PrasadBG05}. Liveness properties (e.g., starvation, deadlock) that contain the LTL operator $F$ are checked by encoding $\neg \phi_{k}$ in a loop within a bounded execution of length at most $k$, such that $\phi$ is violated on each state in the loop. In this case, formula~\ref{bounded-model-checking-biere} can be rewritten as:

@@

\noindent where $\phi_{i}$ is the propositional variable $\phi$ at time step $i$. Thus, this formula can be satisfied if and only if for some $i$ ($i \leq k$) there exists a reachable state at time step $i$ in which $\phi$ is violated.

>>>>

Indeed, given a transition system \textit{M}, which is derived from the control-flow graph of a program, a property $\phi$, which represents program correctness and/or a system's behavior, and an iteration bound \textit{k}, which limits loop unrolling, data structures, and context-switches, BMC techniques thus unfold a system \textit{k} times, in order to convert it into a verification condition $\psi$, which is expressed in propositional logic or in a decidable-fragment of first-order logic, such that $\psi$ is \textit{satisfiable} if and only if $\phi$ has a counterexample of depth less than or equal to \textit{k}. The propositional problem associated with SAT-based BMC is formulated by constructing the following equation~\cite{Biere99}:
%
\begin{equation}
\label{bounded-model-checking-biere}
\psi_{k} = I\left(s_{0}\right) \wedge \bigwedge^{k-1}_{i=0} R\left(s_{i},s_{i+1}\right) \wedge \neg \phi_{k}
\end{equation}

\noindent Here, $\phi_{k}$ represents a safety property $\phi$ in step $k$, $I$ is the set of initial states of $M$, $R\left(s_{i},s_{i+1}\right)$ is the transition relation of $M$ at time steps $i$ and $i+1$. Hence, the equation $\bigwedge^{k-1}_{i=0} R\left(s_{i},s_{i+1}\right)$ represents the set of all executions of $M$ of length $k$. $\neg \phi_{k}$ represents the condition that $\phi$ is violated in state $k$, which is reached by a bounded execution of $M$ of length $k$. Finally, the resulting (bit-vector) equation is translated to conjunctive normal form in linear time and passed to a SAT solver for checking satisfiability. Eq.~(\ref{bounded-model-checking-biere}) can be used to check safety properties~\cite{PrasadBG05}. Liveness properties ({\it e.g.}, starvation, deadlock) that contain the Linear-time Temporal Logic (LTL) operator $F$ are checked by encoding $\neg \phi_{k}$ in a loop within a bounded execution of length at most $k$, such that $\phi$ is violated on each state in the loop. In this case, Eq.~\ref{bounded-model-checking-biere} can be rewritten as:

@@

\noindent where $\phi_{i}$ is the propositional variable $\phi$ at time step $i$. Thus, this equation can be satisfied if and only if for some $i$ ($i \leq k$) there exists a reachable state at time step $i$ in which $\phi$ is violated.
